\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-09 evaluation.tex
some updates all around

\subsection{Stress testing vs \psharp testing}

\setlength{\tabcolsep}{.42em}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rr rrrrr}
\centering
\input{experiments/tables/results.tex}
\end{tabular}
\caption{Results.}
\label{tab:testing}
\end{table*}

Comparison of traditional stress testing VS what we do with \psharp

>>>>

\subsection{Systematic testing with \psharp}

\setlength{\tabcolsep}{.52em}
\begin{table*}[t]
\small
\centering
\begin{tabular}{l rrrr rrrr}
\centering
\input{experiments/tables/results.tex}
\end{tabular}
\caption{Results from running the \psharp random and PCT systematic testing schedulers for 100,000 iterations. We report: time in seconds to find a bug (Time to bug); number of scheduling points when a bug was found (\#SP); percentage of buggy iterations (\%Buggy); and if a bug was found with a particular scheduler (Bug found?).}
\label{tab:testing}
\end{table*}

Table~\ref{tab:testing} presents the results from running the \psharp systematic testing engine on each case study with an enabled bug using the random and the PCT schedulers. We configured the engine to perform 100,000 iterations. The random seed for both schedulers was generated in each iteration using the \texttt{DateTime.Now.Millisecond} API which represents the current time in milliseconds. The PCT scheduler was configured with a bug depth of 2 and a max number of scheduling steps to execute of 500. All reported times are in seconds.

### 2015-09-09 experience.tex
some updates all around

\subsection{Distributed Extent Management System}
\label{sec:cases:azurestore}

@@

\subsection{Live Azure Table Migration}

@@

>>>>

\subsection{Azure Storage vNext}
\label{sec:cases:azurestore}

%Azure Storage vNext is the next generation storage system for Windows Azure. Azure Storage vNext consists of multiple extent managers, extent nodes, and network engines that are able to send messages across the network, and enqueue any received messages in the input queue of the corresponding node (see Figure~\ref{fig:azurestore}). Each extent manager is responsible for managing a subset of the extent nodes. Each extent node stores its corresponding extent in a local storage, and sends periodical heartbeats and synchronization messages to the extent manager. When the extent manager receives a synchronization message it is responsible to update extent nodes with the latest extent.

%The liveness property that must be always eventually satisfied in the Azure Storage vNext system is that a user-defined $N$ number of extent nodes must be always eventually available with the latest extent. There was an actual bug in the system, that led this property to fail for some very rare executions. Although this buggy behavior would be observed from time to time during stress testing, there was no way to reproduce the bug. We discuss later in this paper, how we are able to detect and reproduce this bug using our approach.

%Azure Storage vNext is very challenging to test. All the unit test and integration test suites of the Azure Storage vNext project successfully pass every single time. However, the developers found that the stress test suite, which constantly kills and launches extent nodes, could fail from time to time after very long executions. The observed failure was that the liveness property described in Section~\ref{sec:overview:bugs} would not get satisfied. The developers had no way to deterministically reproduce this bug or be able to detect what is the culprit, as the traces they were getting were very long and hard to parse.

@@

vNext bug goes here.

\subsection{Live Azure Table Migration}
\label{sec:cases:migration}

The Live Azure Table Migration is a library capable of transparently migrating a data set between tables in the Windows Azure storage service while an application is accessing the data set.  MigratingTable provides a \emph{virtual table} with an API similar to that of an ordinary Azure table, backed by a pair of \emph{old} and \emph{new}  tables.  A background \emph{migrator} job moves all data from the old table to the new table.  Meanwhile, each read or write issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol we designed, which guarantees linearizability of operations on the virtual table across multiple application processes assuming that the backend tables respect their own linearizability guarantees.

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{img/livemigration}
\caption{Resharding a data set when a third Azure storage account is added. Two key ranges are each migrated to the new account using a MigratingTable instance (abbreviated MTable).}
\label{fig:livemigration}
\end{figure}

% N.B. Artifact Services is mentioned at http://research.microsoft.com/en-us/people/schulte/.  Hopefully it's OK to reveal that it was the system in this case study. ~ Matt 2015-08-17
The initial motivation for MigratingTable was to solve a scaling problem for Artifact Services, an internal Microsoft system with a data set that is sharded across tables in different Azure storage accounts because it exceeds the limit on traffic supported by a single Azure storage account.  As the traffic continues to grow over time, the system needs to reshard the data set across a greater number of Azure storage accounts without interrupting service.  During such a resharding, our sharding manager will identify each key range that should migrate to a different table, and we will use a separate MigratingTable instance for each such key range to actually perform the migration (Figure~\ref{fig:livemigration}).  MigratingTable may also be useful to migrate data to a table with different values of configuration parameters that Azure does not support changing on an existing table, such as geographic location.

@@

\subsection{An example bug in MigratingTable}
\MMComment{Move wherever appropriate}

One of the bugs in MigratingTable that we found using the \psharp test stands out because it reflects the type of oversight that tends to occur as designs evolve and it's unclear whether we would have been able to find it by any other method (\MMComment{revise remark when we have stress test results?}).  This bug, which we named QueryStreamedBackUpNewStream, is in the implementation of a streaming read from the virtual table, which should return a stream of all rows in the table sorted by key.  The essential implementation idea is to start streams $s_O$, $s_N$ from the old and new backend tables and merge the sorted streams by keeping track of the next row in each stream and returning the row with the lesser key.  In parallel, the migrator job is concurrently copying rows from the old table to the new table; we had satisfied ourselves that this concurrency would not cause any problems.  However, then we added support to the migrator job to delete the old table when it finishes copying, which triggers the virtual stream to close $s_O$.  Suppose the virtual stream is in a state in which the next row in $s_O$ has key $k_O$ and the next row in $s_N$ has key $k_N$, where $k_O < k_N$.  Further suppose that before the next read from the virtual stream, the migrator job copies a row with key $k$ ($k_O < k < k_N$) from the old table to the new table and then deletes the old table.  Since $s_O$ has not yet returned this row when it is closed and $s_N$ has already advanced to $k_N$, the row with key $k$ will be missed by the virtual stream.  A similar problem can occur if $s_N$ does not reflect rows inserted into the new table by the migrator job after $s_N$ is started, as allowed by the IChainTable2 specification.  Restarting $s_N$ when the old table is deleted fixes both variants of the bug.

\MMComment{Add a figure based on migration-bug3-explanation.pptx (probably a hybrid of slides 4 and 5, assuming we want only one figure).}

\subsection{Azure Service Fabric (change to CScale?)}
\label{sec:cases:fabric}

\PDComment{I guess we should write stuff about CScale here based on our last discussion: overview of the system (collection of Fabric services connected via TPL dataflow?), of its environment (Fabric), how they interop?, why its very challenging to test? how they test currently? I am not sure if all these should go here or be split here and the experience report, we will see ... same for the above case studies}

\emph{Azure Service Faric} (or \emph{Fabric} for short) is a platform and API for creating reliable services that execute on a cluster of machines. The developer writes a service that receives requests (e.g.\ from some client program via HTTP) and mutates its state based on these requests. In order to make the service \emph{reliable}, Fabric launches several copies (\emph{replicas}) of the service, where each copy runs as a separate process on different nodes in the cluster. One replica is selected to be the \emph{primary} which serves client requests; the rest are \emph{secondaries}. The primary replicates state changes to the secondaries so that all replicas eventually have the same state. If the primary fails (e.g.\ if the node on which the primary is running crashes), Fabric elects one of the secondaries to be the new primary and launches another secondary; the new secondary will receive a full or partial copy (depending on whether persistent storage is used) of the state of the new primary in order to ``catch up'' with the other secondaries. Fabric provides a name-resolution service so that clients can always find the current primary. Fabric exposes several different APIs that developers can use to write services.
